A Quantitative Study of Finnish Knowledge Production `r params$min.year`-`r params$max.year`

### 2016-09-13 inst/examples/slidetemplates.Rmd
ok

if (!params$catalogue == "all") {
  df0 <- filter(df0, catalog == params$catalogue)
}

if ("paper.consumption.km2" %in% names(df0)) {
  df0$paper <- df0$paper.consumption.km2     
}
```

@@

# Group small publishers
# Top publishers by title count
ntop <- 10
top <- names(top(df, "publisher", ntop))
df$publisher[!df$publisher %in% top] <- "Other"
df$publisher <- factor(df$publisher, c(top, "Other"))

>>>>

if (!params$catalogue == "all") {
  df0 <- filter(df0, catalog == params$catalogue)
}
```

@@

# Group small publishers
# Top publishers by title count
ntop <- 10
top <- names(top(df, "publisher", ntop))
#df$publisher[!df$publisher %in% top] <- "Other"
df <- df %>% filter(publisher %in% top)
df$publisher <- factor(df$publisher, c(top, "Other"))
